Yoghurt under stress

### 2014-06-05 seminaire_Tanakalab.tex
All needed data to make creep figures.\n Yoghurt recipe

\end{frame}

>>>>

\begin{columns}
\column{0.5\textwidth}
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 2,
			xticklabels at=edge bottom,
			vertical sep=0,
			},
		xmode=log,
		xmin=1e2,xmax=3e5,
		scale only axis,
		width=\textwidth-4em,
		height=0.3\textwidth,
		extra tick style={grid=major},%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		]
	\nextgroupplot[
		ymin=0, ymax=7, ylabel={pH},
		%extra y ticks={4.6}, extra y tick labels={},%
		]
	\addplot+[no marks,Accent2] table{Y190_cas4_gdl1.pH};
	\draw[help lines] (axis cs:1e2,4.6) -- (axis cs:1.3979e4,4.6) node[pos=0, below right, font=\scriptsize, text width=0.4\textwidth] {isoelectric point $pH\approx 4.6$}  -- (axis cs:1.3979e4,0);

	\nextgroupplot[
		xlabel={time (s)},
		ymin=0, ylabel={$\textcolor{Accent2}{G^\prime}, \textcolor{Main}{G^{\prime\prime}}$ (\si{\pascal})},
		extra x ticks={1e5}, extra x tick labels={},
		]
	\addplot+[no marks,Accent2] table{cas4_GDL1_Y22.prise};
	\addplot+[no marks,Main] table[y index=2]{cas4_GDL1_Y22.prise};
	\begin{scope}[font=\scriptsize]
		\node[above right] at (rel axis cs:0,0) {casein ``micelles''};
		\draw[<-] (axis cs:1.3979e4,654) -- +(-1em,0) node[left] {gelation};
	\end{scope}
	\end{groupplot}
\end{tikzpicture}

\column{0.5\textwidth}
\includegraphics[width=\textwidth, clip=true, trim=0 0 0 10cm]{MEB_cas4_gdl1_22}

\begin{scriptsize}
\textit{Kaláb (1983),\linebreak Roefs \& van Vliet (1990),\linebreak Lucey \& Singh (1998)}
\end{scriptsize}

\end{columns}
\end{frame}
